DESING AND SIMULATION SOFTWARE FOR RHODOTRON TYPE ELECTRON ACCELERATORS

### 2024-01-07 subsections/future/future_work.tex
Spiral corrected

Rhodotron Simulation, which has been the main focus of this thesis, is ready and waiting to be tested with the cavity that is being manufactured; 
Several improvements and new feature implementations are underway in the meantime:
\iffalse \begin{figure}[H]
    \begin{subfigure}[t]{0.5\textwidth}
        \begin{itemize}
            \item Electric and magnetic field import
            \item Field generator module to directly produce field files from specified cavity
            \item Synchrotron radiation calculations to determine radiation and energy loss
            \item \ee interactions
            \item Redesign of the GUI
            \item 3D render in GUI
        \end{itemize}
    \end{subfigure}
    \begin{subfigure}[t]{0.5\textwidth}
        \begin{itemize}
            \item Refactoring of the \eEM interaction and logging to improve performance
            \item Refactoring of the GUI Render Frame to improve render speed
            \item Refactoring the magnet class to introduce field leaks
            \item Extention of analysis tools in Analyze Frame
            \item $L_{out}$ sweep in Sweep Frame
        \end{itemize}
    \end{subfigure}
\end{figure} \fi
\begin{itemize}
    \item Electric and magnetic field import
    \item Field generator module to directly produce field files from specified cavity
    \item Synchrotron radiation calculations to determine radiation and energy loss
    \item \ee interactions
    \item Redesign of the GUI
    \item 3D render in GUI
    \item Refactoring of the \eEM interaction and logging to improve performance
    \item Refactoring of the GUI Render Frame to improve render speed
    \item Refactoring the magnet class to introduce field leaks
    \item Extention of analysis tools in Analyze Frame
    \item $L_{out}$ sweep in Sweep Frame
\end{itemize}

>>>>

Rhodotron Simulation, which has been the main focus of this thesis, is ready and waiting to be tested with the cavity that is being manufactured; 
Several improvements and new feature implementations are underway in the meantime:
\iffalse \begin{figure}[H]
    \begin{subfigure}[t]{0.5\textwidth}
        \begin{itemize}
            \item Electric and magnetic field import
            \item Field generator module to directly produce field files from specified cavity
            \item Synchrotron radiation calculations to determine radiation and energy loss
            \item \ee interactions
            \item Redesign of the GUI
            \item 3D render in GUI
        \end{itemize}
    \end{subfigure}
    \begin{subfigure}[t]{0.5\textwidth}
        \begin{itemize}
            \item Refactoring of the \eEM interaction and logging to improve performance
            \item Refactoring of the GUI Render Frame to improve render speed
            \item Refactoring the magnet class to introduce field leaks
            \item Extention of analysis tools in Analyze Frame
            \item $L_{out}$ sweep in Sweep Frame
        \end{itemize}
    \end{subfigure}
\end{figure} \fi
\begin{itemize}
    \item Electric and magnetic field import,
    \item Field generator module to directly produce field files from specified cavity,
    \item Synchrotron radiation calculations to determine radiation and energy loss,
    \item \ee interactions,
    \item Redesign of the GUI,
    \item 3D render in GUI,
    \item Refactoring of the \eEM interaction and logging to improve performance,
    \item Refactoring of the GUI Render Frame to improve render speed,
    \item Refactoring the magnet class to introduce field leaks,
    \item Extention of analysis tools in Analyze Frame,
    \item $L_{out}$ sweep in Sweep Frame.
\end{itemize}

### 2024-01-07 subsections/simulation/gui/gui.tex
Spiral corrected

%%%%%%
% Start of intermediate.tex
\clearpage
\section{Graphical User Interface}

Until this point, Rhodotron Simulation could be used with a configration file, defining the problem that would be simulated.
An example of this configuration file can be found in \fromfig{config_file} of \fromapp{example_simulation_runs}. 
\vspace{10pt}
\begin{figure}[H]
    \centering
    \includegraphics[width=\linewidth]{../../../figures/illustrations/RhodoSim_GUI_Draft_V02.pdf}
    \caption{An Illustration of the first GUI design.}
    \label{fig:gui_illustration}
\end{figure}
\clearpage
This approach was simple and fast; however, it was not suitable for the average target user since required basic knowledge of command line interface and was not up to modern standards.
For this reason, a GUI was decided to be built, using ROOT framework. 
This would also enable Rhodotron simulation to make use of analysis tools offered by ROOT.

@@

In the \fromfig{gui_config}, the implemented version of \fromfig{gui_illustration} can be observed. 
Available frames of this version of the GUI are discussed further in the following sections.
\subsection{Simulation Frame}
This frame spawns and manages the simulation engine, configures and starts the simulation. 
It has a progress bar that shows the current progress of the simulation, communucating with UI handler thread in simulation engine.
Simulation frame while a simulation is running can be observed in \fromfig{gui_simulate_1} of \fromapp{supp}.
\clearpage
\subsection{Configuration Frame}
This frame provides an interface for specifying, saving or loading a configuration, consists of $\vecthreeBF{B}$ field, $\vecthreeBF{E}$ field, RF description, \egun, simulation configuration regions.
Each one having an illustration of what the parameters are as can be seen in \fromfig{gui_config}.
\vspace{10pt}
\begin{figure}[h]
    \centering
    \includegraphics[width=\linewidth]{../../../figures/rhodoSim/GUI_config_frame.png}
    \caption{The configuration frame of implementated first GUI design.}
    \label{fig:gui_config}
\end{figure}

\clearpage
\subsection{Render Frame}
Since the rendering capabilities of ROOT is superior than gnuplot, the user can render a playback of the simulation in real time, 
see a specific time frame, export as snapshot or animated gif file.
Two example renders can be seen in \fromfig{gui_render_1} and \fromfig{gui_render_2} of \fromapp{supp}.
\vspace{10pt}
\begin{figure}[h]
    \centering
    \includegraphics[width=0.85\linewidth]{../../../figures/rhodoSim/GUI_render_frame_5.png}
    \caption{Render frame of GUI.}
    \label{fig:gui_render_1}
\end{figure}

\subsection{Analyze Frame}
Analyze frame provides tools for analyzing and visualizing the simulation data. 
In the current version, energy distribution histogram and \textbf{E(t)} graph of each electron are implementated into this frame.
This frame is a work in progress and will be the focus of improvement and become a really powerfull tool in the near future.
In \fromfig{gui_analyze_Edist}, Analyze Frame plotting energy distribution histogram, and in \fromfig{gui_analyze_Et} and \fromfig{gui_analyze_Et2} of \fromapp{supp}, Analyze Frame plotting \textbf{E(t)} graphs can be observed.
\vspace{10pt}
\begin{figure}[h!]
    \centering
    \includegraphics[width=0.8\linewidth]{../../../figures/rhodoSim/GUI_analyze_Edist_2.png}
    \caption{Analyze frame of GUI E distribution.}
    \label{fig:gui_analyze_Edist}
\end{figure}

\begin{figure}[h!]
    \centering
    \includegraphics[width=0.9\linewidth]{../../../figures/rhodoSim/GUI_analyze_Et_3.png}
    \caption{Analyze frame of GUI E(t).}
    \label{fig:gui_analyze_Et}
    \vspace{20pt}
\end{figure}

@@

It takes the range of sweep, draws $\phi_{lag}$ vs $\mu E$, $\phi_{lag}$ vs $\sigma E$ and $\phi_{lag}$ vs $\sigma R$ mentioned in \fromsec{philag_sweep}.
This enables user with an already built accelerator to optimize \egun parameters quickly. 
In the \fromfigf{gui_sweep_muE}{gui_sweep_sE}{gui_sweep_running}{gui_sweep_sR} of \fromapp{supp}, this frame can be inspected in detail.
\vspace{10pt}
\begin{figure}[h]
    \centering
    \includegraphics[width=0.85\linewidth]{../../../figures/rhodoSim/GUI_sweep_muE_3.png}
    \caption{Sweep frame of GUI $\phi_{lag}$ $\mu E$ result.}
    \label{fig:gui_sweep_muE}
\end{figure}
\clearpage
\begin{figure}[h]
    \centering
    \includegraphics[width=0.85\linewidth]{../../../figures/rhodoSim/GUI_sweep_sE_3.png}
    \caption{Sweep frame of GUI $\phi_{lag}$ sweep $\sigma E$ result.}
    \label{fig:gui_sweep_sE}
    \vspace{10pt}
\end{figure}

>>>>

%%%%%%
% Start of intermediate.tex
\section{Graphical User Interface}

Until this point, Rhodotron Simulation could be used with a configration file, defining the problem that would be simulated.
An example of this configuration file can be found in \fromfig{config_file} of \fromapp{example_simulation_runs}.

This approach was simple and fast; however, it was not suitable for the average target user since required basic knowledge of command line interface and was not up to modern standards.
For this reason, a GUI was decided to be built, using ROOT framework. 
This would also enable Rhodotron simulation to make use of analysis tools offered by ROOT.

@@

In the \fromfig{gui_config}, the implemented version of \fromfig{gui_illustration} can be observed. 
Available frames of this version of the GUI are discussed further in the following sections.
\vspace{-10pt}
\begin{figure}[H]
    \centering
    \includegraphics[width=\linewidth]{../../../figures/illustrations/RhodoSim_GUI_Draft_V02.pdf}
    \vspace{-20pt}
    \caption{An Illustration of the first GUI design.}
    \label{fig:gui_illustration}
\end{figure}

\subsection{Simulation Frame}
This frame spawns and manages the simulation engine, configures and starts the simulation. 
It has a progress bar that shows the current progress of the simulation, communucating with UI handler thread in simulation engine.
Simulation frame while a simulation is running can be observed in \fromfig{gui_simulate_1}.

\begin{figure}[H]
    \centering
    \includegraphics[width=0.85\linewidth]{./figures/rhodoSim/GUI_simulation_frame.png}
    \vspace{-20pt}
    \caption{Simulate frame of \textit{GUI}.}
    \label{fig:gui_simulate_1}
\end{figure}

\clearpage
\subsection{Configuration Frame}
This frame provides an interface for specifying, saving or loading a configuration, consists of $\vecthreeBF{B}$ field, $\vecthreeBF{E}$ field, RF description, \egun, simulation configuration regions.
Each one having an illustration of what the parameters are as can be seen in \fromfig{gui_config}.
\vspace{10pt}
\begin{figure}[h]
    \centering
    \includegraphics[width=\linewidth]{../../../figures/rhodoSim/GUI_config_frame.png}
    \vspace{-30pt}
    \caption{The configuration frame of implementated first GUI design.}
    \label{fig:gui_config}
\end{figure}

\clearpage
\subsection{Render Frame}
Since the rendering capabilities of ROOT is superior than gnuplot, the user can render a playback of the simulation in real time, 
see a specific time frame, export as snapshot or animated gif file.
Two example renders can be seen in \fromfig{gui_render_1} and \fromfig{gui_render_2} of \fromapp{supp}.
\vspace{10pt}
\begin{figure}[h]
    \centering
    \includegraphics[width=0.85\linewidth]{../../../figures/rhodoSim/GUI_render_frame_5.png}
    \vspace{-20pt}
    \caption{Render frame of GUI.}
    \label{fig:gui_render_1}
\end{figure}

\subsection{Analyze Frame}
Analyze frame provides tools for analyzing and visualizing the simulation data. 
In the current version, energy distribution histogram and \textbf{E(t)} graph of each electron are implementated into this frame.
This frame is a work in progress and will be the focus of improvement and become a really powerfull tool in the near future.
In \fromfig{gui_analyze_Edist}, Analyze Frame plotting energy distribution histogram, and in \fromfig{gui_analyze_Et} and \fromfig{gui_analyze_Et2} of \fromapp{supp}, Analyze Frame plotting \textbf{E(t)} graphs can be observed.
\vspace{10pt}
\begin{figure}[h!]
    \centering
    \includegraphics[width=0.8\linewidth]{../../../figures/rhodoSim/GUI_analyze_Edist_2.png}
    \vspace{-20pt}
    \caption{Analyze frame of GUI E distribution.}
    \label{fig:gui_analyze_Edist}
\end{figure}

\begin{figure}[h!]
    \centering
    \includegraphics[width=0.9\linewidth]{../../../figures/rhodoSim/GUI_analyze_Et_3.png}
    \vspace{-20pt}
    \caption{Analyze frame of GUI E(t).}
    \label{fig:gui_analyze_Et}
    \vspace{20pt}
\end{figure}

@@

It takes the range of sweep, draws $\phi_{lag}$ vs $\mu E$, $\phi_{lag}$ vs $\sigma E$ and $\phi_{lag}$ vs $\sigma R$ mentioned in \fromsec{philag_sweep}.
This enables user with an already built accelerator to optimize \egun parameters quickly. 
In the \fromfigf{gui_sweep_muE}{gui_sweep_sE}{gui_sweep_running}{gui_sweep_sR} of \fromapp{supp}, this frame can be inspected in detail.
\vspace{10pt}
\begin{figure}[h]
    \centering
    \includegraphics[width=0.85\linewidth]{../../../figures/rhodoSim/GUI_sweep_muE_3.png}
    \vspace{-20pt}
    \caption{Sweep frame of GUI $\phi_{lag}$ $\mu E$ result.}
    \label{fig:gui_sweep_muE}
\end{figure}
\clearpage
\begin{figure}[h]
    \centering
    \includegraphics[width=0.85\linewidth]{../../../figures/rhodoSim/GUI_sweep_sE_3.png}
    \vspace{-20pt}
    \caption{Sweep frame of GUI $\phi_{lag}$ sweep $\sigma E$ result.}
    \label{fig:gui_sweep_sE}
    \vspace{10pt}
\end{figure}
